Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-05 ecoop/content/appendix.tex
directories for conferences

\begin{lemma}\label{lem:ccrectop}
   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a dataflow fact such that there exists a realizable path $p\in\textsf{RP}(n,\,d)$. Let $T$ be the set of all types in the program.
   If there exists a receiver $r\in R$ such that
  \[
    \ccedgefn{\{r\}}(p)(\topcc)(r)=\top_T\,,                       
  \]
  then $r\in \rcc$.
\end{lemma}
\begin{proof} 
Observe that if there is a supergraph path from a method call with signature $s$ to the start of $f$, then the set $\tau(s,\,f)$ is always non-empty.
  Let $r.c()$ be a call on a receiver $r\in R$ with a method signature $s$ to a function $f$.
  If the call site is monomorphic, then $\tau(s,\,f)$ contains all types $T'\subseteq T$ that are compatible with the static type of $r$.
  If the call site is polymorphic, then $\tau(s,\,f)\subset T'$, since some types $t\in T'$ cause dispatch to a method other than~$f$.

@@

\begin{lemma}\label{lem:ccrectop}
   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a dataflow fact such there exists a realizable path $p\in\textsf{RP}(n,\,d)$.
   Then, if there exists a receiver $r\in R$, such that
  \[
    \resultIDE\left(\transCC_{\{r\}}(P)\right)(n)(d)(r)=\top_T\,,
  \]
  then $r\in \rcc$.
\end{lemma}
\begin{proof}
  As shown in~\eqref{eq:resultThroughEdgefn},
  \[
    \resultIDE\left(\transCC_{\{r\}}(P)\right)(n)(d)(r)=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
  \]
  Since the latter is equal to $\top_T$, it follows that for each realizable path $p'$ to node $n$, $\ccedgefn{\{r\}}(p')(\top)(r)=\top_T$. According to~Lemma~\ref{lem:ccrectop}, this is only possible if $r\in\rcc$.
\end{proof}

>>>>

\begin{lemma}\label{lem:ccrectop}
   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a data-flow fact such that there exists a realizable path $p\in\textsf{RP}(n,\,d)$. Let $T$ be the set of all types in the program.
   If there exists a receiver $r\in R$ such that
  \[
    \ccedgefn{\{r\}}(p)(\topcc)(r)=\top_T\,,                       
  \]
  then $r\in \rcc$.
\end{lemma}
\begin{proof} 
Observe that if there is a supergraph path from a method call with signature $s$ to the start of $f$, then the set $\tau(s,\,f)$ is always non-empty.
  Let $r.c()$ be a call on a receiver $r\in R$ with a method signature $s$ to a function $f$.
  If the call site is monomorphic, then $\tau(s,\,f)$ contains all types $T'\subseteq T$ that are compatible with the static type of $r$.
  If the call site is polymorphic, then $\tau(s,\,f)\subset T'$, since some types $t\in T'$ cause dispatch to a method other than~$f$.

@@

\begin{lemma}\label{lem:ccrectop}
   For an IFDS problem $P$, let $n\in N^*$ be a node, and $d\in D$ a data-flow fact such there exists a realizable path $p\in\textsf{RP}(n,\,d)$.
   Then, if there exists a receiver $r\in R$, such that
  \[
    \resultIDE\left(\transCC_{\{r\}}(P)\right)(n)(d)(r)=\top_T\,,
  \]
  then $r\in \rcc$.
\end{lemma}
\begin{proof}
  As shown in~\eqref{eq:resultThroughEdgefn},
  \[
    \resultIDE\left(\transCC_{\{r\}}(P)\right)(n)(d)(r)=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\,.
  \]
  Since the latter is equal to $\top_T$, it follows that for each realizable path $p'$ to node $n$, $\ccedgefn{\{r\}}(p')(\top)(r)=\top_T$. According to~Lemma~\ref{lem:ccrectop}, this is only possible if $r\in\rcc$.
\end{proof}

### 2015-03-05 ecoop/content/impl.tex
directories for conferences

\subsubsection{Defining an IFDS Problem}\label{sec:ifdsdef}
Recall that an IFDS problem instance is defined as a five-tuple
\[
    (G^*,\ D,\ F,\ M_F,\,\sqcap)\,,
\]
where $G^*=(N^*,\,E^*)$ is the control-flow supergraph of the program, $D$ is the set of dataflow facts, $F\subseteq2^D\to2^D$ is a set of distributive dataflow functions, and the function $$M_F:\,E^*\to(2^D\to2^D)$$ maps the supergraph edges to dataflow functions, and is extended to paths by composition.

@@

\subsubsection{Defining an IDE Problem}\label{sec:defide}
An IDE problem instance is a four-tuple
\[
    (G^*,\ D,\ L,\ \menv),
\]
where $G^*$ and $D$ are defined in the same way as for IFDS. $L$ is a finite-height lattice that represents the values to which dataflow facts are mapped in an IDE problem. An environment $Env(D, L)$ maps dataflow facts to lattice elements. Finally, the map $$M_{\textsf{Env}}:\,E^*\to(\textsf{Env}(D, L)\to \textsf{Env}(D, L))$$ is a function from the control-flow-supergraph edges to environment transformers, extended to paths by composition.

@@

%\paragraph{Lattice Elements}
In the correlated-calls transformation, the 
%Just like in the equivalence transformation $\transEq$, the exploded supergraph for $\transCC$ is the same as in the original IFDS problem. The 
lattice elements are maps from receivers to sets of types:
    $\lcc=\left\{\,m:\ R\to2^T\right\}$,
where $R$ is the set of receivers and $T$ is the set of all types.
For each receiver~$r$, the map gives an overapproximation of the possible
runtime types of $r$.
Sets of types are ordered by the superset relation, and this is lifted to maps from receivers
to sets of types, so the bottom element $\botcc$ maps every receiver to the set of all types,
and the top element $\topcc$ maps every receiver to the empty set of types.
During an actual execution, every receiver $r$ points to an object of some
runtime type. Therefore, a data flow fact
is unreachable along any feasible path if its corresponding lattice element
maps any receiver to the empty set of types.

@@

We can now define $\edgefn$, which assigns a micro-function to each edge in
the exploded supergraph. 
Along a $\mathbf0$-edge, the micro function is the identity. 
All other functions can be described with $\varepsilon_S$.
On a ``diagonal'' edge from $\mathbf0$ to a non-$\mathbf0$ fact that corresponds
to some data flow fact becoming reachable, $\varepsilon_S(e)$ is applied to the initial
map $\botcc$ that conservatively allows every receiver to point to an object of any type.
On all other edges, $\varepsilon_S(e)$ is applied to the existing map before the edge.
The is formalized in the following definition.
\begin{definition}\label{def:edgefn}
For each edge $e = (n_1,d_1) \to (n_2,d_2)$, $\ccedgefn S(e)$ is defined as follows:
  \begin{equation}\label{eq:edgefndef}
      \ccedgefn S(e)=
        \begin{cases}
          \id  &\text{if $d_1=d_2=\mathbf0$},\\
          \lambda m\,.\,\varepsilon_S(e)(\botcc) &\text{if $d_1=\mathbf0$ and $d_2\ne\mathbf0$},\\
          \lambda m\,.\,\varepsilon_S(e)(m)  &\text{otherwise.}
        \end{cases}
  \end{equation}
  %We define both $\ccedgefn S$ and $\varepsilon_S$ to be extended to paths by composition.
\end{definition}

@@

The composition of these micro functions results in the empty set as the possible
types of the receiver \code{a}, indicating that this data flow path that would
result in an information leak is actually infeasible.
\end{example}

@@

In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data flow path is
infeasible. Therefore, a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
converted to an IFDS result as follows:
\begin{equation}\label{eq:transCcDef}
    \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.
\end{equation}
%\otodo{In Equation (5), I changed $\rho(n)(d)$ to $\rho(n)(d)(r)$, because I think
%    the original was incorrect. Marianna, please check that this correction is correct.}

>>>>

\subsubsection{Defining an IFDS Problem}\label{sec:ifdsdef}
Recall that an IFDS problem instance is defined as a five-tuple
\[
    (G^*,\ D,\ F,\ M_F,\,\sqcap)\,,
\]
where $G^*=(N^*,\,E^*)$ is the control-flow supergraph of the program, $D$ is the set of data-flow facts, $F\subseteq2^D\to2^D$ is a set of distributive data-flow functions, and the function $$M_F:\,E^*\to(2^D\to2^D)$$ maps the supergraph edges to data-flow functions, and is extended to paths by composition.

@@

\subsubsection{Defining an IDE Problem}\label{sec:defide}
An IDE problem instance is a four-tuple
\[
    (G^*,\ D,\ L,\ \menv),
\]
where $G^*$ and $D$ are defined in the same way as for IFDS. $L$ is a finite-height lattice that represents the values to which data-flow facts are mapped in an IDE problem. An environment $Env(D, L)$ maps data-flow facts to lattice elements. Finally, the map $$M_{\textsf{Env}}:\,E^*\to(\textsf{Env}(D, L)\to \textsf{Env}(D, L))$$ is a function from the control-flow-supergraph edges to environment transformers, extended to paths by composition.

@@

%\paragraph{Lattice Elements}
In the correlated-calls transformation, the 
%Just like in the equivalence transformation $\transEq$, the exploded supergraph for $\transCC$ is the same as in the original IFDS problem. The 
lattice elements are maps from receivers to sets of types:
    $\lcc=\left\{\,m:\ R\to2^T\right\}$,
where $R$ is the set of receivers and $T$ is the set of all types.
For each receiver~$r$, the map gives an overapproximation of the possible
runtime types of $r$.
Sets of types are ordered by the superset relation, and this is lifted to maps from receivers
to sets of types, so the bottom element $\botcc$ maps every receiver to the set of all types,
and the top element $\topcc$ maps every receiver to the empty set of types.
During an actual execution, every receiver $r$ points to an object of some
runtime type. Therefore, a data-flow fact
is unreachable along any feasible path if its corresponding lattice element
maps any receiver to the empty set of types.

@@

We can now define $\edgefn$, which assigns a micro-function to each edge in
the exploded supergraph. 
Along a $\mathbf0$-edge, the micro function is the identity. 
All other functions can be described with $\varepsilon_S$.
On a ``diagonal'' edge from $\mathbf0$ to a non-$\mathbf0$ fact that corresponds
to some data-flow fact becoming reachable, $\varepsilon_S(e)$ is applied to the initial
map $\botcc$ that conservatively allows every receiver to point to an object of any type.
On all other edges, $\varepsilon_S(e)$ is applied to the existing map before the edge.
The is formalized in the following definition.
\begin{definition}\label{def:edgefn}
For each edge $e = (n_1,d_1) \to (n_2,d_2)$, $\ccedgefn S(e)$ is defined as follows:
  \begin{equation}\label{eq:edgefndef}
      \ccedgefn S(e)=
        \begin{cases}
          \id  &\text{if $d_1=d_2=\mathbf0$},\\
          \lambda m\,.\,\varepsilon_S(e)(\botcc) &\text{if $d_1=\mathbf0$ and $d_2\ne\mathbf0$},\\
          \lambda m\,.\,\varepsilon_S(e)(m)  &\text{otherwise.}
        \end{cases}
  \end{equation}
  %We define both $\ccedgefn S$ and $\varepsilon_S$ to be extended to paths by composition.
\end{definition}

@@

The composition of these micro functions results in the empty set as the possible
types of the receiver \code{a}, indicating that this data-flow path that would
result in an information leak is actually infeasible.
\end{example}

@@

In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data-flow path is
infeasible. Therefore, a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
converted to an IFDS result as follows:
\begin{equation}\label{eq:transCcDef}
    \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.
\end{equation}
%\otodo{In Equation (5), I changed $\rho(n)(d)$ to $\rho(n)(d)(r)$, because I think
%    the original was incorrect. Marianna, please check that this correction is correct.}

### 2015-03-05 ecoop/content/intro.tex
directories for conferences

Since a CFG is an over-approximation of the possible flows 
of control in concrete executions of a program, it may contain \textit{infeasible} 
paths that cannot occur at runtime. The precision of a data-flow analysis algorithm
depends critically on its ability to detect and disregard such infeasible paths.
The popular \textit{Interprocedural Finite Distributive Subset} (IFDS) algorithm 
by  Reps, Horwitz, and Sagiv~\cite{reps1995precise} is a general data-flow analysis
algorithm for computing solutions to standard finite distributive data-flow problems such 
as reaching definitions, available expressions, and taint analysis.
A distinguishing 
characteristic of IFDS is that it avoids infeasible interprocedural paths in which calls 
and returns to/from functions are not properly matched. Sagiv, Reps, and Horwitz
also presented the \textit{Interprocedural Distributive Environment} (IDE) algorithm
\cite{sagiv1996precise} that similarly only considers properly matched call/return
edges, but that supports a broader range of dataflow problems by expanding the 
domain of flow functions to \textit{environments} that go beyond the data-flow facts 
considered by IFDS.

This paper presents an approach to dataflow analysis that avoids a type
of infeasible path that arises in object-oriented programs when two or more
methods are dynamically dispatched on the same receiver object.
%\mtodo{Should we define the term ``receiver''?}
In such cases, if the
method calls are polymorphic (i.e., if they dispatch to different method definitions 
depending on the type of the receiver expression at run time), then their dispatch 
behaviours will be correlated. A recent paper~\cite{DBLP:journals/scp/Tip15} identified
this problem but did not present a concrete solution or algorithm, and we are not aware 
of any existing dataflow analysis that is capable of avoiding infeasible paths that arise 
in the presence of correlated method calls.

@@

The approach taken in our work is to transform a standard IFDS problem into an
IDE problem that precisely accounts for infeasible paths due to correlated calls. 
The results of this IDE problem can be mapped back to the dataflow domain of the 
original IFDS problem.

>>>>

Since a CFG is an over-approximation of the possible flows 
of control in concrete executions of a program, it may contain \textit{infeasible} 
paths that cannot occur at runtime. The precision of a data-flow analysis algorithm
depends critically on its ability to detect and disregard such infeasible paths.
The popular \textit{Interprocedural Finite Distributive Subset} (IFDS) algorithm 
by  Reps, Horwitz, and Sagiv~\cite{reps1995precise} is a general data-flow analysis
algorithm for computing solutions to standard finite distributive data-flow problems such 
as reaching definitions, available expressions, and taint analysis.
A distinguishing 
characteristic of IFDS is that it avoids infeasible interprocedural paths in which calls 
and returns to/from functions are not properly matched. Sagiv, Reps, and Horwitz
also presented the \textit{Interprocedural Distributive Environment} (IDE) algorithm
\cite{sagiv1996precise} that similarly only considers properly matched call/return
edges, but that supports a broader range of data-flow problems by expanding the 
domain of flow functions to \textit{environments} that go beyond the data-flow facts 
considered by IFDS.

This paper presents an approach to data-flow analysis that avoids a type
of infeasible path that arises in object-oriented programs when two or more
methods are dynamically dispatched on the same receiver object.
%\mtodo{Should we define the term ``receiver''?}
In such cases, if the
method calls are polymorphic (i.e., if they dispatch to different method definitions 
depending on the type of the receiver expression at run time), then their dispatch 
behaviours will be correlated. A recent paper~\cite{DBLP:journals/scp/Tip15} identified
this problem but did not present a concrete solution or algorithm, and we are not aware 
of any existing data-flow analysis that is capable of avoiding infeasible paths that arise 
in the presence of correlated method calls.

@@

The approach taken in our work is to transform a standard IFDS problem into an
IDE problem that precisely accounts for infeasible paths due to correlated calls. 
The results of this IDE problem can be mapped back to the data-flow domain of the 
original IFDS problem.

### 2015-03-05 ecoop/figures/fig-examplesupergraph.tex
directories for conferences

%inter-procedural edges
  \path[->,dashed,ultra thick] (call_foo) edge[out=20,in=190] (st_a_foo);
  \path[->,dashed] (call_foo) edge[color=lightsalmonpink,out=-20,in=135] (st_b_foo);
  \path[->,dashed] (call_bar) edge[out=25,in=220] (st_a_bar);
  \path[->,dashed,ultra thick] (call_bar) edge[color=lightsalmonpink,out=18,in=160] (st_b_bar);
  \path[->,dashed,ultra thick] (end_a_foo) edge[out=220,in=15] (return_foo);
  \path[->,dashed] (end_b_foo) edge[color=lightsalmonpink,out=160,in=-60] (return_foo);
  \path[->,dashed] (end_a_bar) edge[out=210,in=40] (return_bar);
  \path[->,dashed,ultra thick] (end_b_bar) edge[color=lightsalmonpink,out=200,in=-40] (return_bar);

%arrow description
    \node [description] (intra_arrow_left) [above left = 2*\dist and 3.5*\dist of st_a_bar] {};
    \node [description] (intra_arrow_right) [right = \dist of intra_arrow_left] {};
    \node [description] (inter_arrow_left) [below = .5*\dist of intra_arrow_left] {};
    \node [description] (inter_arrow_right) [below = .5*\dist of intra_arrow_right] {};
    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intra-procedural edge} (intra_arrow_right);
    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{inter-procedural edge} (inter_arrow_right); 
}
\end{tikzpicture}
   \end{minipage}
   \vspace*{-25mm}
  \caption{
    Control flow supergraph for the example program of Figure~\ref{list:ccexample}.
    An infeasible path is shown in bold. 
  }%
  \label{fig:examplesupergraph}%
\end{figure}

>>>>

%interprocedural edges
  \path[->,dashed,ultra thick] (call_foo) edge[out=20,in=190] (st_a_foo);
  \path[->,dashed] (call_foo) edge[color=lightsalmonpink,out=-20,in=135] (st_b_foo);
  \path[->,dashed] (call_bar) edge[out=25,in=220] (st_a_bar);
  \path[->,dashed,ultra thick] (call_bar) edge[color=lightsalmonpink,out=18,in=160] (st_b_bar);
  \path[->,dashed,ultra thick] (end_a_foo) edge[out=220,in=15] (return_foo);
  \path[->,dashed] (end_b_foo) edge[color=lightsalmonpink,out=160,in=-60] (return_foo);
  \path[->,dashed] (end_a_bar) edge[out=210,in=40] (return_bar);
  \path[->,dashed,ultra thick] (end_b_bar) edge[color=lightsalmonpink,out=200,in=-40] (return_bar);

%arrow description
    \node [description] (intra_arrow_left) [above left = 2*\dist and 3.5*\dist of st_a_bar] {};
    \node [description] (intra_arrow_right) [right = \dist of intra_arrow_left] {};
    \node [description] (inter_arrow_left) [below = .5*\dist of intra_arrow_left] {};
    \node [description] (inter_arrow_right) [below = .5*\dist of intra_arrow_right] {};
    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intraprocedural edge} (intra_arrow_right);
    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{interprocedural edge} (inter_arrow_right); 
}
\end{tikzpicture}
   \end{minipage}
   \vspace*{-25mm}
  \caption{
    Control flow supergraph for the example program of Figure~\ref{list:ccexample}.
    An infeasible path is shown in bold. 
  }%
  \label{fig:examplesupergraph}%
\end{figure}

### 2015-03-05 oopsla/content/abstract.tex
directories for conferences

\begin{abstract}
    When two methods are invoked on the same object, the dispatch behaviours of these
    method calls will be correlated. If two correlated method calls are polymorphic 
    (i.e., they dispatch to different method definitions depending on the type of 
    the receiver object), a program's interprocedural control flow graph
    will contain infeasible paths. Existing algorithms for dataflow analysis 
    are unable to ignore such infeasible paths, giving rise to loss of precision.

	We show how infeasible paths due to correlated calls can be eliminated for 
	\textit{Interprocedural Finite Distributive Subset} (IFDS) problems, a large class 
	of data-flow analysis problems with broad applications. Our approach is to
	transform an IFDS problem into an \textit{Interprocedural Distributive 
	Environment} (IDE) problem, in which edge functions are designed in a
	way that enables us to ignore dataflow along infeasible paths. A solution
	to this IDE problem can be mapped back to the solution space of the original
	IFDS problem.
        We formalize the approach, prove it correct, and report on an implementation
        in the WALA analysis framework.
\end{abstract}

>>>>

\begin{abstract}
    When two methods are invoked on the same object, the dispatch behaviours of these
    method calls will be correlated. If two correlated method calls are polymorphic 
    (i.e., they dispatch to different method definitions depending on the type of 
    the receiver object), a program's interprocedural control flow graph
    will contain infeasible paths. Existing algorithms for data-flow analysis 
    are unable to ignore such infeasible paths, giving rise to loss of precision.

	We show how infeasible paths due to correlated calls can be eliminated for 
	\textit{Interprocedural Finite Distributive Subset} (IFDS) problems, a large class 
	of data-flow analysis problems with broad applications. Our approach is to
	transform an IFDS problem into an \textit{Interprocedural Distributive 
	Environment} (IDE) problem, in which edge functions are designed in a
	way that enables us to ignore data flow along infeasible paths. A solution
	to this IDE problem can be mapped back to the solution space of the original
	IFDS problem.
        We formalize the approach, prove it correct, and report on an implementation
        in the WALA analysis framework.
\end{abstract}

### 2015-03-05 oopsla/content/related.tex
directories for conferences

Sridharan et~al.'s improvements to the precision of pointer analysis
for JavaScript programs~\cite{DBLP:conf/ecoop/SridharanDCST12} also
eliminate infeasible paths. However, instead of infeasible paths
between dynamically dispatched method calls, their approach eliminates
infeasible paths between reads and writes of different properties
(the JavaScript analogue of fields) of an object. Unlike in more static languages,
property names in JavaScript are first class values (strings). When a loop indexed by
property names updates the properties of objects, the loop body is extracted into a function
and analyzed context sensitively with a separate context for each property name.
The approach differs from ours in that it targets points-to analysis rather
than IFDS analyses, in that it targets infeasible paths due to different
property names rather than different dynamically dispatched methods,
and in that it employs context sensitivity to improve precision.

>>>>

Sridharan et~al.'s improvements to the precision of pointer analysis
for Ja\-va\-Script programs~\cite{DBLP:conf/ecoop/SridharanDCST12} also
eliminate infeasible paths. However, instead of infeasible paths
between dynamically dispatched method calls, their approach eliminates
infeasible paths between reads and writes of different properties
(the JavaScript analogue of fields) of an object. Unlike in more static languages,
property names in JavaScript are first class values (strings). When a loop indexed by
property names updates the properties of objects, the loop body is extracted into a function
and analyzed context sensitively with a separate context for each property name.
The approach differs from ours in that it targets points-to analysis rather
than IFDS analyses, in that it targets infeasible paths due to different
property names rather than different dynamically dispatched methods,
and in that it employs context sensitivity to improve precision.

### 2015-03-05 oopsla/figures/fig-cc_edge_fn_example.tex
directories for conferences

    \node [n,label=$r$] (st_a_foo_p) [left=\nd of st_a_foo.west] {};
    \node [n] (return_secret_p) [left=\nd of return_secret.west] {};
    \node [n] (end_a_foo_p) [left=\nd of end_a_foo.west] {};
    \node [n,label=$\mathbf0$] (st_a_foo_z) [left=\nd of st_a_foo_p] {};
    \node [n] (return_secret_z) [left=\nd of return_secret_p] {};
    \node [n] (end_a_foo_z) [left=\nd of end_a_foo_p] {};
%A.foo method edges
    \path[->, ultra thick](st_a_foo_z) edge (return_secret_z); 
    \path[->](return_secret_z) edge node[arrowtext,near start,above right=0.4cm and -.15cm,rotate=-60]{$\lambda m.\botcc$} (end_a_foo_z); 
    \path[->,dashed, ultra thick](call_foo_z) edge [out=38,in=238]  (st_a_foo_z);
    \path[->,dashed](end_a_foo_z) edge [out=200,in=43] (return_foo_z);
    \path[->,dashed, ultra thick](end_a_foo_p) edge  [out=200,in=43] node[arrowtext,below,rotate=30]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (return_foo_v);
    \path[->](st_a_foo_p) edge (return_secret_p); 
    \path[->](return_secret_p) edge (end_a_foo_p);
    \path[->, ultra thick](return_secret_z) edge (end_a_foo_p);

@@

    \node [n,label=\texttt{s}] (st_a_bar_s) [left=\nd of st_a_bar.west] {};
    \node [n,label=$\mathbf0$] (st_a_bar_z) [left=\nd of st_a_bar_s] {};
    \node [n] (end_a_bar_s) [left=\nd of end_a_bar.west] {};    
    \node [n] (end_a_bar_z) [left=\nd of end_a_bar_s] {};
%A.bar method edges
    \path[->](st_a_bar_z) edge (end_a_bar_z);
    \path[->,dashed](call_bar_z) edge [out=20,in=229] (st_a_bar_z);
    \path[->,dashed](end_a_bar_z) edge [out=220,in=35] (return_bar_z);
    \path[->](st_a_bar_s) edge (end_a_bar_s);
    \path[->,dashed](call_bar_v) edge [out=20,in=230] node[arrowtext,near end,above left=-.1cm and -.15cm,rotate=36]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (st_a_bar_s);

>>>>

    \node [n,label=$r$] (st_a_foo_p) [left=\nd of st_a_foo.west] {};
    \node [n] (return_secret_p) [left=\nd of return_secret.west] {};
    \node [n] (end_a_foo_p) [left=\nd of end_a_foo.west] {};
    \node [n,label=$\mathbf0$] (st_a_foo_z) [left=\nd of st_a_foo_p] {};
    \node [n] (return_secret_z) [left=\nd of return_secret_p] {};
    \node [n] (end_a_foo_z) [left=\nd of end_a_foo_p] {};
%A.foo method edges
    \path[->, ultra thick](st_a_foo_z) edge (return_secret_z); 
    \path[->](return_secret_z) edge node[arrowtext,near start,above right=0.4cm and -.1cm,rotate=-60]{$\lambda m.\botcc$} (end_a_foo_z); 
    \path[->,dashed, ultra thick](call_foo_z) edge [out=38,in=238]  (st_a_foo_z);
    \path[->,dashed](end_a_foo_z) edge [out=200,in=43] (return_foo_z);
    \path[->,dashed, ultra thick](end_a_foo_p) edge  [out=200,in=43,] node[arrowtext,rotate=28,below=.1cm]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (return_foo_v);
    \path[->](st_a_foo_p) edge (return_secret_p); 
    \path[->](return_secret_p) edge (end_a_foo_p);
    \path[->, ultra thick](return_secret_z) edge (end_a_foo_p);

@@

    \node [n,label=\texttt{s}] (st_a_bar_s) [left=\nd of st_a_bar.west] {};
    \node [n,label=$\mathbf0$] (st_a_bar_z) [left=\nd of st_a_bar_s] {};
    \node [n] (end_a_bar_s) [left=\nd of end_a_bar.west] {};    
    \node [n] (end_a_bar_z) [left=\nd of end_a_bar_s] {};
%A.bar method edges
    \path[->](st_a_bar_z) edge (end_a_bar_z);
    \path[->,dashed](call_bar_z) edge [out=20,in=229] (st_a_bar_z);
    \path[->,dashed](end_a_bar_z) edge [out=220,in=35] (return_bar_z);
    \path[->](st_a_bar_s) edge (end_a_bar_s);
    \path[->,dashed](call_bar_v) edge [out=20,in=230] node[arrowtext,near end,above left=-.1cm and -.15cm,rotate=34]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (st_a_bar_s);
